%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% My Resume
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{my-resume-openfont}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Prasad}{Chandrashekar}
{ Woodland Hills
| \href{mailto:prasad.c82@gmail.com}{prasad.c82@gmail.com}
| 747.263.3190 \\
}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %
% %     Summary
% %
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \summary
% {
%     \custombold{
%         Around 20 Yrs of experience in Software Development \& Test.\\
%         Currently working for LocaliQ (formerly ReachLocal, On H1B Visa with Approved I140).\\
%         Extensive experience in building \& maintaining single page applications esp. using React, Angular \& Redux.\\
%         Adept in collaborating with cross-functional teams \& delivering projects on-time.
%     }
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

\descript{Specialties:}
Typescript \textbullet{} JavaScript (ES6/ES7) \\
HTML5 \textbullet{} CSS3 \\
\location{Familiar with:}
Ruby
\sectionsep

\descript{Libraries/Frameworks}
React \textbullet{} Redux \\
Angular \textbullet{} AngularJS \\
Material-UI \\
Bootstrap \textbullet{} Sass \\
\location{Familiar with:}
Rails \textbullet{} Ionic \textbullet{} jQuery
\sectionsep

\descript{Testing}
Jest \textbullet{} Jasmine \textbullet{} Karma
\sectionsep

\descript{Databases}
MySQL
\sectionsep

\descript{Tools}
Webpack \textbullet{} NPM \\
ESLint  \\
Chrome Dev Tools  \\
Git
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\descript{Sri Siddhartha Institute Of Technology}
\location{BE in Electronics \& Communications}
\location{April 2003 | Tumkur, India}
\location{ Cum. GPA: 69 / 100 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Links
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github: \href{https://github.com/prasadc82}{prasadc82} \\
LinkedIn: \href{https://www.linkedin.com/in/prasadchandrashekar}{prasadchandrashekar} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{LocaliQ / ReachLocal}
\descript{| Engineering Lead }
\location{Nov 2016 – Present | Woodland Hills, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item{Currently developing new UI features for LocaliQ Dash, an AI-powered lead management solution, utilizing React, Material-UI styled components, and ChartJS.}
\item{Led front-end development of sales enablement tools (Google Ads Grader, Facebook Ads Grader, Keyword Tool) leveraging the same React stack with a reusable component architecture.}
\item{Held technical ownership of migrating LocaliQ Grader from AngularJS to Angular 17, significantly enhancing code maintainability and application performance.}
\item{Contribute periodic feature development to the Angular application, utilizing NGXS for state management, RxJS for reactive programming, and lazy loading for performance optimization.}
\item{Integrated authentication mechanisms with Okta and Microsoft Entra ID, supporting secure, role-based access control.}
\item{Collaborated closely with the design team on rebranding initiatives to modernize UI aesthetics and improve user experience.}
\item{Initially developed LocaliQ Grader using AngularJS, Google Maps, ChartJS, jsPDF, and Bootstrap to support sales teams in digital strategy analysis and proposal generation.}
\item{Perform code reviews, oversee CI/CD pipeline management, and lead sprint demos to ensure delivery of high-quality software.}
\end{tightemize}
\sectionsep

\runsubsection{Reachlocal Services Private Limited}
\descript{| Lead Software Engineer }
\location{Apr 2013 – Nov 2016 | Mumbai, India}
\begin{tightemize}
\item{Developed the front end of the order management tool (QTC) using AngularJS and Bootstrap with a component-based architecture.}
\item{Implemented internationalization (i18n) support for the Proposal Tool built with Ruby on Rails and AngularJS.}
\item{Delivered new features and resolved bugs for the Proposal Tool, ensuring product quality and reliability.}
\item{Performed code reviews, managed deployments, and participated actively in sprint demos.}
\end{tightemize}
\sectionsep

\runsubsection{Narus INC}
\descript{| Senior Software Engineer}
\location{Jun 2010 – Apr 2013 | Bangalore, India}
\begin{tightemize}
\item{Developed and implemented new features for the Cyber-Protection Portal, built with Ruby on Rails and Vanilla JavaScript.}
\item{Performed bug fixes, authored unit and end-to-end (E2E) tests, and managed deployment processes.}
\end{tightemize}
\sectionsep

\runsubsection{EFI}
\descript{| Software Engineer}
\location{Sep 2006 – Jun 2010 | Bangalore, India}
\begin{tightemize}
\item{Developed new features for the Capp App, built on Ruby on Rails.}
\item{Addressed bug fixes, wrote unit and end-to-end (E2E) tests, and managed deployment activities.}
\end{tightemize}
\sectionsep

% \runsubsection{CA Technologies}
% \descript{| QA Engineer}
% \location{Aug 2004 – Sep 2006 | Hyderabad, India}
% \begin{tightemize}
% \item{Created comprehensive test cases for Harvest SCM to ensure functionality and reliability.}
% \item{Automated the regression test suite to improve testing efficiency and consistency.}
% \end{tightemize}
% \sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
